### 2018-07-12 Sections/classical_networking_protocols.tex
Minor index

Key examples for the use of UDP are realtime audio and video transmission. If a packet associated with a frame in a video link is delayed and arrives several frames late, it is useless, since it is associated strictly with a previous frame in the video that has already passed. Quality control, in the form of contacting the sender to request a retransmission, would therefore achieve nothing. This applies similarly to live audio streaming, such as voice-over-IP (VoIP), where the late arrival of a packet cannot possibly be correctly inserted into the audio playback and might as well be discarded.

>>>>

Key examples for the use of UDP are realtime audio and video transmission. If a packet associated with a frame in a video link is delayed and arrives several frames late, it is useless, since it is associated strictly with a previous frame in the video that has already passed. Quality control, in the form of contacting the sender to request a retransmission, would therefore achieve nothing. This applies similarly to live audio streaming, such as voice over IP (VoIP)\index{Voice over IP}, where the late arrival of a packet cannot possibly be correctly inserted into the audio playback and might as well be discarded.

### 2018-07-12 Sections/costs_and_attributes_in_quantum_networks.tex
Minor index

A quantum process cannot increase the mutual information between two parties. This yields the \textit{data processing inequality} that, for a sequence of channels \mbox{$X\to Y\to Z$},
\begin{align}\index{Data processing inequality}
I(X:Z)&\leq I(X:Y), \nonumber \\
I(X:Z)&\leq I(Y:Z),
\end{align}
with equality if and only if the channel not specified in the identity on the right hand side (\mbox{$Y\to Z$} or \mbox{$X\to Y$} respectively) is unitary, i.e one of the links in the chain perfectly preserves information content.

The mutual information is defined as being between a particular known pair of states. Of course, in a quantum network we will seldom know what the states being communicated are and will therefore be unable to directly calculate the mutual information. To address this, the \textit{classical channel capacity} of a channel is defined as,
\begin{align}\index{Channel capacity}
\mathcal{C}(\mathcal{E}) = \max_{\hat\rho} [I(\hat\rho,\mathcal{E}(\hat\rho))],
\end{align}
with the intuitive interpretation as the maximum mutual information between input and output states that can be achieved for the channel. (Note: this definition of `capacity' is not to be confused with that which we later refer to in flow networks).

>>>>

A quantum process cannot increase the mutual information between two parties. This yields the \textit{data processing inequality}\index{Data processing inequality} that, for a sequence of channels \mbox{$X\to Y\to Z$},
\begin{align}\index{Data processing inequality}
I(X:Z)&\leq I(X:Y), \nonumber \\
I(X:Z)&\leq I(Y:Z),
\end{align}
with equality if and only if the channel not specified in the identity on the right hand side (\mbox{$Y\to Z$} or \mbox{$X\to Y$} respectively) is unitary, i.e one of the links in the chain perfectly preserves information content.

The mutual information is defined as being between a particular known pair of states. Of course, in a quantum network we will seldom know what the states being communicated are and will therefore be unable to directly calculate the mutual information. To address this, the \textit{classical channel capacity}\index{Classical channel capacity} of a channel is defined as,
\begin{align}\index{Channel capacity}
\mathcal{C}(\mathcal{E}) = \max_{\hat\rho} [I(\hat\rho,\mathcal{E}(\hat\rho))],
\end{align}
with the intuitive interpretation as the maximum mutual information between input and output states that can be achieved for the channel. (Note: this definition of `capacity' is not to be confused with that which we later refer to in flow networks).

### 2018-07-12 Sections/introduction.tex
Minor index

\begin{itemize}
	\item Searching unstructured databases (Sec.~\ref{sec:quantum_search}):\index{Grover's algorithm}
		\begin{itemize}
		\item Grover's algorithm \cite{bib:Grover96}.
		\item Quadratic speedup.
		\end{itemize}
	\item Satisfiability \& optimisation problems\footnote{A satisfiability problem is one where we search a function's input space for a solution(s) satisfying a given output constraint. The hardest such problems, like the archetypal 3-\textsc{SAT}\index{3-SAT problem} problem, are \textbf{NP}-complete.}\index{\textbf{NP} \& \textbf{NP}-complete} (Sec.~\ref{sec:optimising_the_world}):
		\begin{itemize}
			\item Grover's algorithm.
			\item Quadratic speedup.
			\item Includes solving \textbf{NP}-complete problems, and brute-force cracking of private encryption keys.\index{Satisfiability problems}
			\item Many optimisation problems are \textbf{NP}-complete or can be approximated in \textbf{NP}-complete.\index{Optimisation problems}
			\end{itemize}
	\item Period finding and integer factorisation\index{Shor's algorithm} (Sec.~\ref{sec:shors_alg}):
		\begin{itemize}
		\item Shor's algorithm \cite{bib:ShorFactor}.
		\item Exponential speedup.
		\item This compromises Rivest, Shamir \& Adleman (RSA) public-key cryptography \cite{bib:RSA}\index{RSA encryption}\index{Public-key encryption}, the most widely used cryptographic protocol on the internet today.
		\end{itemize}
	\item Simulation of quantum systems\index{Quantum simulation} (Sec.~\ref{sec:quantum_sim_alg}):
		\begin{itemize}
			\item Lloyd's algorithm \cite{bib:lloyd1996universal}.
			\item Exponential speedup.
			\item This includes simulation of: molecular and atomic interactions in the study of quantum chemistry or nuclear physics; interactions between drug molecules and organic molecules for drug design; genetic interactions for the study of genetics and genetic medicine; nanoscale semiconductor physics for integrated circuit design; and much more.
			\end{itemize}
	\item Simulation of quantum field theories\index{Simulating quantum field theories}:
		\begin{itemize}
		 \item Jordan-Lee-Preskill algorithm \cite{bib:JLP, bib:RohdeWavelet15}
		 \item Exponential speedup.
		 \item A key area of fundamental physics research.
		 \end{itemize}
	\item Topological big-data analysis (Sec.~\ref{sec:TDA}):\index{Topological big-data analysis}
		\begin{itemize}
		\item Lloyd's algorthm \cite{bib:lloyd2016quantum, USTCexperiment}.
		\item Exponential speedup.
		\item Broad applications including: social media network analysis; consumer behaviour; behavioural dynamics; neuroscience; and higher-dimensional signal and image processing.
		\end{itemize}
	\item Solving linear systems of equations (Sec.~\ref{sec:linear_systems}):\index{Linear systems}
		\begin{itemize}
		\item \comment{To do} \cite{bib:harrow2009quantum, bib:BerryLinear}.
		\item Exponential speedup.
		\item Widespread applications in linear algebra and calculus.
		\end{itemize}
	\item Quantum machine learning (Sec.~\ref{sec:quantum_mind}):\index{Quantum machine learning}
		\begin{itemize}
		\item Lloyd's algorithm \cite{bib:lloyd2013quantum}.
		\item This includes putting an end to humanity \latinquote{Ne obliviscaris.}
		\end{itemize}
\end{itemize}
An elementary technical overview of some of these archetypal algorithms is presented in Sec.~\ref{sec:quantum_algs}.

@@

\begin{figure}[!htb]
	\includegraphics[width=0.5\textwidth]{complexity_classes}\index{Complexity classes} \index{\textbf{P} \& \textbf{BPP}} \index{\textbf{NP} \& \textbf{NP}-complete} \index{\textbf{BQP} \& \textbf{BQP}-complete} \index{\textbf{\#P} \& \textbf{\#P}-complete}
	\caption{Believed relationships between the complexity classes most relevant to quantum computing. \textbf{BPP} is the class of polynomial-time probabilistic classical algorithms. \textbf{NP} is the class of problems verifiable in polynomial time using classical algorithms. \textbf{NP}-complete are the subset of \textbf{NP} problems polynomial-time reducible to any other problem in \textbf{NP}, similarly for other `complete' problems. \textbf{BQP} is the class of probabilistic algorithms solvable in polynomial time on universal quantum computers. $\#\mathbf{P}$ is the set of counting problems, that count satisfying solutions to \textbf{P} problems (\textbf{P} is the same as \textbf{BPP}, but deterministic, rather than probabilisitic). \textbf{EXP} is the class of all algorithms that require exponential time. Note that it is actually unproven whether \mbox{$\mathbf{P}=\mathbf{BPP}$} or \mbox{$\mathbf{P}\subset\mathbf{BPP}$}. There are examples where the best known \textbf{BPP} algorithms outperform the best known \textbf{P} algorithms, which could arise because the two classes are inequivalent, or that we simply haven't tried hard enough to find the best deterministic algorithms. Furthermore, while it is known that \mbox{$\mathbf{P}\subseteq\mathbf{NP}$}, it is not known whether \mbox{$\mathbf{BPP}\subseteq\mathbf{NP}$}. For the sake of illustration in our Venn diagram we have taken the view that it is. \textbf{BPP} is regarded as the class of problems efficiently solvable on universal Turing machines (i.e classical computers), whereas \textbf{BQP} is that efficiently solvable on universal quantum computers. The computational superiority of quantum computers is based on the (strongly believed, yet unproven) assumption that \mbox{$\mathbf{BPP}\subset\mathbf{BQP}$}.} \label{fig:complexity_classes}
\end{figure}

>>>>

\begin{itemize}
	\item Searching unstructured databases (Sec.~\ref{sec:quantum_search}):\index{Grover's algorithm}
		\begin{itemize}
		\item Grover's algorithm \cite{bib:Grover96}.
		\item Quadratic speedup.
		\end{itemize}
	\item Satisfiability \& optimisation problems\footnote{A satisfiability problem is one where we search a function's input space for a solution(s) satisfying a given output constraint. The hardest such problems, like the archetypal 3-\textsc{SAT}\index{3-SAT problem} problem, are \textbf{NP}-complete.}\index{\textbf{NP} \& \textbf{NP}-complete}\index{Optimisation problems}\index{Satisfiability problems} (Sec.~\ref{sec:optimising_the_world}):
		\begin{itemize}
			\item Grover's algorithm.
			\item Quadratic speedup.
			\item Includes solving \textbf{NP}-complete problems, and brute-force cracking of private encryption keys.\index{Satisfiability problems}
			\item Many optimisation problems are \textbf{NP}-complete or can be approximated in \textbf{NP}-complete.\index{Optimisation problems}
			\end{itemize}
	\item Period finding and integer factorisation\index{Shor's algorithm} (Sec.~\ref{sec:shors_alg}):
		\begin{itemize}
		\item Shor's algorithm \cite{bib:ShorFactor}.
		\item Exponential speedup.
		\item This compromises Rivest, Shamir \& Adleman (RSA) public-key cryptography \cite{bib:RSA}\index{RSA encryption}\index{Public-key encryption}, the most widely used cryptographic protocol on the internet today.
		\end{itemize}
	\item Simulation of quantum systems\index{Quantum simulation} (Sec.~\ref{sec:quantum_sim_alg}):
		\begin{itemize}
			\item Lloyd's algorithm \cite{bib:lloyd1996universal}.
			\item Exponential speedup.
			\item This includes simulation of: molecular and atomic interactions in the study of quantum chemistry or nuclear physics; interactions between drug molecules and organic molecules for drug design; genetic interactions for the study of genetics and genetic medicine; nanoscale semiconductor physics for integrated circuit design; and much more.
			\end{itemize}
	\item Simulation of quantum field theories\index{Simulating quantum field theories}:
		\begin{itemize}
		 \item Jordan-Lee-Preskill algorithm \cite{bib:JLP, bib:RohdeWavelet15}
		 \item Exponential speedup.
		 \item A key area of fundamental physics research.
		 \end{itemize}
	\item Topological data analysis (Sec.~\ref{sec:TDA}):\index{Topological data analysis}
		\begin{itemize}
		\item Lloyd's algorthm \cite{bib:lloyd2016quantum, USTCexperiment}.
		\item Exponential speedup.
		\item Broad applications including: social media network analysis\index{Social media network analysis}; consumer behaviour\index{Consumer behaviour}; behavioural dynamics\index{Behavioural dynamics}; neuroscience\index{Neuroscience}; and higher-dimensional signal and image processing\index{Signal \& image processing}.
		\end{itemize}
	\item Solving linear systems of equations (Sec.~\ref{sec:linear_systems}):\index{Linear systems}
		\begin{itemize}
		\item \comment{To do} \cite{bib:harrow2009quantum, bib:BerryLinear}.
		\item Exponential speedup.
		\item Widespread applications in linear algebra and calculus.
		\end{itemize}
	\item Quantum machine learning (Sec.~\ref{sec:quantum_mind}):\index{Quantum machine learning}
		\begin{itemize}
		\item Lloyd's algorithm \cite{bib:lloyd2013quantum}.
		\item This includes putting an end to humanity \latinquote{Ne obliviscaris.}
		\end{itemize}
\end{itemize}
An elementary technical overview of some of these archetypal algorithms is presented in Sec.~\ref{sec:quantum_algs}.

@@

\begin{figure}[!htb]
	\includegraphics[width=0.5\textwidth]{complexity_classes}\index{Complexity classes} \index{\textbf{P} \& \textbf{BPP}} \index{\textbf{NP} \& \textbf{NP}-complete} \index{\textbf{BQP} \& \textbf{BQP}-complete} \index{\textbf{\#P} \& \textbf{\#P}-complete} \index{\textbf{EXP} \& \textbf{EXP}-complete}
	\caption{Believed relationships between the complexity classes most relevant to quantum computing. \textbf{BPP} is the class of polynomial-time probabilistic classical algorithms. \textbf{NP} is the class of problems verifiable in polynomial time using classical algorithms. \textbf{NP}-complete are the subset of \textbf{NP} problems polynomial-time reducible to any other problem in \textbf{NP}, similarly for other `complete' problems. \textbf{BQP} is the class of probabilistic algorithms solvable in polynomial time on universal quantum computers. $\#\mathbf{P}$ is the set of counting problems, that count satisfying solutions to \textbf{P} problems (\textbf{P} is the same as \textbf{BPP}, but deterministic, rather than probabilisitic). \textbf{EXP} is the class of all algorithms that require exponential time. Note that it is actually unproven whether \mbox{$\mathbf{P}=\mathbf{BPP}$} or \mbox{$\mathbf{P}\subset\mathbf{BPP}$}. There are examples where the best known \textbf{BPP} algorithms outperform the best known \textbf{P} algorithms, which could arise because the two classes are inequivalent, or that we simply haven't tried hard enough to find the best deterministic algorithms. Furthermore, while it is known that \mbox{$\mathbf{P}\subseteq\mathbf{NP}$}, it is not known whether \mbox{$\mathbf{BPP}\subseteq\mathbf{NP}$}. For the sake of illustration in our Venn diagram we have taken the view that it is. \textbf{BPP} is regarded as the class of problems efficiently solvable on universal Turing machines (i.e classical computers), whereas \textbf{BQP} is that efficiently solvable on universal quantum computers. The computational superiority of quantum computers is based on the (strongly believed, yet unproven) assumption that \mbox{$\mathbf{BPP}\subset\mathbf{BQP}$}.} \label{fig:complexity_classes}
\end{figure}

### 2018-07-12 Sections/optimising_the_world.tex
Minor index

\begin{figure}[!htb]
\includegraphics[width=0.35\textwidth]{graph_colouring}\\
\includegraphics[width=0.35\textwidth]{four_colouring}
\caption{(top) Example of a graph with 3-colouring, such that no two vertices connected by an edge share the same colour. For this particular graph, 3-colouring is optimal (in the sense that the number of colours in minimised). It can easily be seen upon inspection that no 2-colouring is possible for this graph. Thus, this graph's chromatic number is \mbox{$\chi(G)=3$}\index{Chromatic number}. (bottom) A 4-colouring of the states of France\index{Elderberries}. Any planar map such as this has a chromatic number of at most 4 -- the `four colour theorem'.}\index{Graph colouring}\label{fig:graph_colouring}	
\end{figure}

>>>>

\begin{figure}[!htb]
\includegraphics[width=0.35\textwidth]{graph_colouring}\\
\includegraphics[width=0.35\textwidth]{four_colouring}
\caption{(top) Example of a graph with 3-colouring, such that no two vertices connected by an edge share the same colour. For this particular graph, 3-colouring is optimal (in the sense that the number of colours in minimised). It can easily be seen upon inspection that no 2-colouring is possible for this graph. Thus, this graph's chromatic number is \mbox{$\chi(G)=3$}\index{Chromatic number}. (bottom) A 4-colouring of the states of France\index{Elderberries}. Any planar map such as this has a chromatic number of at most 4 -- the `four colour theorem'.}\index{Graph colouring}\index{Surrender}\label{fig:graph_colouring}	
\end{figure}

### 2018-07-12 Sections/quality_of_service.tex
Minor index

\begin{figure}[!htb]
	\begin{align}
		\Qcircuit @C=.7em @R=.4em @! {
		\lstick{} & \qw & \targ & \meter \\
		\lstick{} & \qw & \ctrl{-1} & \qw
		} \nonumber
	\end{align}
	\caption{Construction of a parity measurement circuit using a single CNOT gate and a single-qubit measurement. The measurement outcome indicates whether the two input qubits were the same (\mbox{$\ket{0}\ket{0}$}, \mbox{$\ket{1}\ket{1}$}) or different (\mbox{$\ket{0}\ket{1}$}, \mbox{$\ket{1}\ket{0}$}). See Sec.~\ref{sec:bell_proj} for a simple linear optics construction for this operation.}\label{fig:parity_meas}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.39\textwidth]{entanglement_purification}
\caption{Protocol for entanglement purification of two noisy Bell-pairs (blue) into a single less noisy Bell-pair. Not shown are trivial single-qubit local corrections that may need to be made, depending upon measurement outcomes.} \label{fig:ent_purif_circ}
\end{figure}

@@

In \cite{RohdeHaselgrove} a derivation of a generalisation of the quantum Hamming bound\index{Quantum Hamming bound} was presented, where the number of located and unlocated errors were treated as independent parameters. They found that for non-degenerate codes the Hamming bound allows exactly twice as many located as unlocated errors. Specifically, for $t_l$ located errors and $t_u$ unlocated errors in an $n$-qubit non-degenerate code encoding $k$ logical qubits, QEC is possible provided that the number of errors satisfied,
\begin{align}
\sum_{i=0}^{t_u + \lfloor t_l/2 \rfloor} \binom{n}{i}3^i 2^k \leq 2^n.
\end{align}
\comment{Explain Hamming bound, potentially in footnote. Explain what degenerate and non-degenerate codes are.}

>>>>

\begin{figure}[!htb]
	\begin{align}
		\Qcircuit @C=.7em @R=.4em @! {
		\lstick{} & \qw & \targ & \meter \\
		\lstick{} & \qw & \ctrl{-1} & \qw
		} \nonumber
	\end{align}
	\caption{Construction of a parity measurement circuit using a single CNOT gate and a single-qubit measurement. The measurement outcome indicates whether the two input qubits were the same (\mbox{$\ket{0}\ket{0}$}, \mbox{$\ket{1}\ket{1}$}) or different (\mbox{$\ket{0}\ket{1}$}, \mbox{$\ket{1}\ket{0}$}). See Sec.~\ref{sec:bell_proj} for a simple linear optics construction for this operation.}\label{fig:parity_meas}\index{Parity measurement}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.39\textwidth]{entanglement_purification}
\caption{Protocol for entanglement purification of two noisy Bell-pairs (blue) into a single less noisy Bell-pair. Not shown are trivial single-qubit local corrections that may need to be made, depending upon measurement outcomes.} \label{fig:ent_purif_circ}\index{Entanglement purification protocol}
\end{figure}

@@

In \cite{RohdeHaselgrove} a derivation of a generalisation of the quantum Hamming bound\index{Quantum Hamming bound} for non-degenerate\footnote{In a non-degenerate code, all correctable errors map the codeword to orthogonal states. For degenerate codes\index{Degenerate codes} multiple distinct errors can map the codeword to the same state. The Hamming bound exploits the non-degeneracy using a counting or `pigeonholing' argument to count correctable errors.} QEC codes\index{Non-degenerate codes} was presented, where the number of located and unlocated errors were treated as independent parameters. They found that for non-degenerate codes the Hamming bound allows exactly twice as many located as unlocated errors. Specifically, for $t_l$ located errors and $t_u$ unlocated errors in an $n$-qubit non-degenerate code encoding $k$ logical qubits, QEC is possible provided that the number of errors satisfied,
\begin{align}
\sum_{i=0}^{t_u + \lfloor t_l/2 \rfloor} \binom{n}{i}3^i 2^k \leq 2^n.
\end{align}
